%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience \faBriefcase }


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}

\cventry
  { McGill University and CTA (Advanced Technology Research Center by \textbf{BRP})  } 
  {Ph.D. Candidate} 
  {Sherbrookes, Quebec, Canada} % Location
  {Sept 2024 - Today} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Developed AI control systems and precise algorithms in Unity using Python and C\#.
      \item Applied Sim2Real techniques with Unity and ROS2 for seamless transitions.
      \item Designed point cloud processing algorithms in C++ for LiDAR-based collision avoidance in autonomous vehicles.
      \item Deployed AI models on Jetson Nano for embedded robotics applications.
      \item Built neural networks with PyTorch for advanced robotics solutions.
      \item Standardized code deployment workflows using Docker for consistent development environments.
      \item Managed robot communication over Ethernet for real-time control.
    \end{cvitems}
  }



\cventry
  { CTA (Advanced Technology Research Center by \textbf{BRP}) } 
  {AI and Robotics Researcher} 
  {Sherbrooke, Quebec, Canada} % Location
  {May 2024 - Sept 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Developed AI algorithms (computer vision and imitation learning) for robotics applications using PyTorch.
      \item Designed and implemented nodes in ROS2 for real-time robotics control and prototyping.
      \item Developed drivers in C++ for automotive-grade Continental radar with UDP communication.
      \item Managed real-time robot communication over Ethernet, optimizing latency and data reliability.
      \item Processed and filtered point clouds for enhanced perception capabilities in robotics systems.
      \item Implemented debugging and performance analysis using tools such as oscilloscopes and signal analyzers.
    \end{cvitems}
  }

\cventry
    {Tesla} 
    { Robotics Systems Integration Engineer} 
    {Palo Alto, California, United States} % Location
    {Nov 2023 - April 2024 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Developed firmware for STM32 microcontrollers, utilizing C and VS Code for low-level programming.
        \item Automated firmware testing pipelines using Python (Pytest) and Golang.
        \item Integrated communication protocols such as CAN, CAN-FD, and Ethernet for robot actuators.
        \item Designed and customized Docker environments to support scalable CI/CD pipelines.
        \item Configured Jenkins servers for continuous integration and automated firmware validation.
        \item Conducted hardware debugging and system bring-up using oscilloscopes and JTAG tools.
        \item Collaborated with cross-functional teams to integrate motor control algorithms and robotic actuators.
      \end{cvitems}
    }

\cventry
    {Tesla} 
    {Car Computer Test and Reliability Engineer Intern} 
    {Palo Alto, California, United States} % Location
    {Sept 2022 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Designed an $I^2C$ driver from scratch in C for automotive-grade ASICs.
        \item Programmed Python scripts to automate testing on embedded Linux systems.
        \item Designed and debugged PCBs (Altium) incorporating high-speed interfaces like SPI, I2C, and Ethernet.
        \item Characterized signal integrity using oscilloscopes and logic analyzers.
        \item Developed embedded software for STM32F7 microcontrollers (ARM Cortex-M7).
        \item Implemented TCP server-host communication systems in C for real-time data transmission.
        \item Conducted hardware validation and debugging during board bring-up.
      \end{cvitems}
    }

\cventry
    {INO ( Institut National d'Optique)} 
    {Computer Vision and AI Researcher (Master's Candidate)} 
    {Quebec City, Quebec, Canada} % Location
    {Jan 2021 - Aug 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Designed real-time embedded AI solutions for image processing on Jetson Xavier AGX.
        \item Developed and optimized image segmentation algorithms using frameworks like PyTorch and TensorFlow.
        \item Modified and implemented advanced AI architectures: U-Net, Mask R-CNN, and DeepLabV3.
        \item Benchmarked multiple segmentation models to determine the best one for our application.
        \item Integrated Basler cameras with C++ and Python for real-time image acquisition and processing.
        \item Optimized AI inference pipelines for low-latency embedded systems.
        \item Characterized image quality and developed tools for parameter tuning.
        \item Designed control software for near infrared sensor systems.
      \end{cvitems}
    }

\cventry
    {ABB} % Job title
    {Electronic Designer} % Organisation
    {Quebec City, Quebec, Canada} % Location
    {Aug 2021 - Sept 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Updated PCB designs (schematic and layout) to address obsolescence using Altium.
        \item Designed and debugged high-speed PCBs and analog circuits for industrial applications.
        \item Characterized photodiode signal performance using oscilloscopes and other diagnostic tools.
        \item Participated in the board bring-up process for space-grade PCBs, ensuring high reliability.
        \item Developed embedded software in C and Python for hardware control and diagnostics.
        \item Designed cable harnesses and ensured compliance with in-house standards.
        \item Utilized SVN for version control and collaboration.
      \end{cvitems}
    }



%---------------------------------------------------------

%  \cventry
%    {Photonic and laser optics center } % Job title
%    {Hardware/Firmware designer (Part-time : 15h/week)} % Organisation
%    {Quebec City, Quebec, Canada} % Location
%    {Jan 2021 - Jul 2021} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%\item Electronic component integration
%\item Selecting multiple electrical components to add safety to the set-up
%\item Development of a power supply system
%\item Testing of extreme weather conditions (-40C)
%\item Embedded software design on a STM32 with $I{2}C$ and UART (Interrupt)
%\item Designed a driver to use an ADC in DMA
%\item High-level software design (Python)
%\item Code sharing on GitHub
%      \end{cvitems}
%    }
%---------------------------------------------------------
%  \cventry
%    {Software developer intern } % Job title
%    {Orthogone Technologies} % Organisation
%    {Dorval, Quebec, Canada} % Location
%    {May 2020 - Aug 2019} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%\item Design automated quality tests in Python %(TestComplete)
%\item Project management with Microsoft Azure
%\item Software sharing through GitKraken
%\item Introduction to Javascript
%\item Develop functions for a communication application in C ++ (QT)
%      \end{cvitems}
%    }
%---------------------------------------------------------
%  \cventry
%    {CREAFORM} % Job title
%    {Hardware/Test Designer intern} % Organisation
%    {Lévis, Quebec, Canada} % Location
%    {Aug 2019 - Dec 2019} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%\item Replace or repair required components on PCBs
%\item Make the assembly of different types of cables
%\item Update software, firmware, and hardware according to published ECNs
%\item Take measurements and start-up reports of electronic charts
%\item Develop test tools to accelerate the implementation of PCBs
%\item Edit prototypes
%\item Electronic component integration
%\item Creation of electronic components library
%\item Design graphical interfaces in order to automate tests
%\item Electronic Board Design with USB 2.0 Communication, I2C, and UART (Altium 2019)
%\item Full embedded software design in C$\sharp$ (PSOC Creator, ARM-Cortex M3)
%\item Design of a low noise power supply circuit
%\item FPGA programming on a PSOC5 chip (PSOC Creator)
%      \end{cvitems}
%    }
%---------------------------------------------------------

%   \cventry
%     {Orthogone Technologies} % Job title
%     {Embedded System Design Intern } % Organisation
%     {Dorval, Quebec, Canada} % Location
%     {Jan 2019 - Apr 2019} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
% \item Design certain software components to be integrated into the final product (PyCharm, MCUXpresso
% Config Tools, Beagle Bone Black, ARM Cortex-M4)
% \item Perform proof of concept
% \item Embedded programming: C, Bash, Python
% \item Perform quality/hardware performance tests (PCB) and software (Malfunction Correction)
% \item Partially design and integrate electronic circuits
% \item Use Git to share my code work)
%       \end{cvitems}
%     }
%---------------------------------------------------------
\end{cventries}
